---
title: "Case Study 2: Wealth and Life Expectancy (Gapminder)"
author: "Tanner Fackrell"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: 
    code_folding: hide
    fig_align: center
    fig_height: 6
    fig_width: 12
    keep_md: yes
    toc: yes
    toc_float: yes
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(dplyr)
library(gapminder)
library(ggplot2)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!

```

## Background

During this Case study I learned a lot about how ggplot works.I learned to use functions that I had never used before. I also learned a lot about how I can find answers to questions I have about using R. It helped me to think of different ways that data can be visualized and why it is done in that way. Finally, I believe that it was helpful because I have a better idea of other possible ways to visualize data.



## Data Visualization

```{r plot_data}
# Plot 1
ggplot(data = filter(gapminder, country != "Kuwait"),
       mapping = aes(x=lifeExp, y=gdpPercap, 
      color = continent, size = pop / 100000)) + 
  geom_point() +
  facet_wrap(~year, nrow = 1) + 
theme_bw() + labs(x = "Life Expectancy", y = "GDP per capita") + 
labs(size = "Population (100k)") +
  scale_y_continuous(trans = "sqrt")
ggsave("Case Study2.png", width = 15, units = "in")
```


```{r}
#Plot 2
gapminder2 <- gapminder %>% group_by(continent, year) %>% mutate(avegdp = weighted.mean(gdpPercap, pop), total_pop= sum(pop)/100000)

ggplot(data = filter(gapminder2, country != "Kuwait"),
       mapping = aes(x=year, y= gdpPercap, color = continent)) +
  geom_line(aes(group = country)) +
  geom_point() +
  facet_wrap(~continent, nrow = 1) +
  theme_bw() + labs(x = "Year", y = "GDP per Capita") + labs(size = "Population (100k)") +
  geom_line(data = gapminder2, mapping = aes(x = year, y = avegdp), color = "black") +
  geom_point(data = gapminder2, mapping = aes(x = year, y = avegdp, size = total_pop), color = "black")

ggsave("Case Studytwo.png", width = 15, units = "in")


```

